\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-05-05 main.tex
writting results part two

\subsection{Expected and stochastic payoffs in $2 \times 2$ games}\label{section:2_by_2_games}

@@

In the game stage, each individual is randomly matched with some other
individual in the population. Their interaction lasts for a number of turns
which is not fixed but depends on the continuation probability \(\delta\). At
each turn the individuals choose between cooperation (\(C\)) and defection
(\(D\)). Thus, there are four possible outcomes in each turn \(CC, CD, DC\) and
\(DD\). If both players cooperate they receive the reward payoff \(R\), whereas
if both players defect they receive the punishment payoff \(P\). If one
cooperates but the other defects, the defector receives the temptation to
defect, \(T\), whereas the cooperator receives the sucker's payoff, \(S\).
Let $\mathcal{U}=\{R,S,T,P\}$ denote the set of feasible payoffs in each round,
and let $\mathbf{u}\!=\!(R,S,T,P)$ be the corresponding payoff vector.

The values of the payoffs are not only based on the prisoner's dilemma but all
the symmetric \(2 \times 2\) games, Table~\ref{table:social_dilemmas}.

\begin{table}[!htbp]
  \begin{center}
    \resizebox{.65\textwidth}{!}{
    \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{ccc}
  \toprule
  & \textbf{social dilemmas} & \textbf{payoffs' constrains} \\
  \midrule
(i) & stage hunt  & \(R > T > P > S\) \\
(ii) & snowdrift  & \(T > R > S > P\) \\
(iii) & harmony  & \(R > T > S > P\) \\
(iv) & prisoner dilemma  & \(T > R > P > S\) \\
(v)& donation game  & \(T > R > P > S\) \& \(T=b, R=b-c, S=-c, P=0\) \\
  \bottomrule
      \end{tabular}}
  \end{center}
  \caption{\textbf{Social dilemmas and payoffs' constrains}. The various social
  dilemmas we explore in this work. Results for cases (i) - (iv) were presented
  in section~\ref{section:2_by_2_games} and results for case (v) were presented
  in section~\ref{section:donation}.}
  \label{table:social_dilemmas}
\end{table}

>>>>

\subsection{Effect of updating payoffs in different social dilemmas}\label{section:2_by_2_games}

By focusing on the donation game in the previous section, we have gained
insights into the possible effects of the updating payoffs, and how parameters
such as the benefit and the strength of selection might can exaggerate the
effect. However, by focusing on one specific game can narrow our knowledge of
the effects of updating payoffs on the different forms of possible human
interactions and social dilemmas. For this reason we explore not only the 
donation game but all the possible symmetric games. These are given by
Table~\ref{table:social_dilemmas}.

\begin{table}[!htbp]
  \begin{center}
    \resizebox{.6\textwidth}{!}{
    \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{ccc}
  \toprule
  & \textbf{social dilemmas} & \textbf{payoffs' constrains} \\
  \midrule
(i) & stage hunt  & \(R > T > P > S\) \\
(ii) & snowdrift  & \(T > R > S > P\) \\
(iii) & harmony  & \(R > T > S > P\) \\
(iv) & prisoner dilemma  & \(T > R > P > S\) \\
(v)& donation game  & \(T > R > P > S\) \& \(T=b, R=b-c, S=-c, P=0\) \\
  \bottomrule
      \end{tabular}}
  \end{center}
  \caption{\textbf{Social dilemmas and payoffs' constrains}. The various social
  dilemmas we explore in this work. Results for cases (i) - (iv) are presented
  in section~\ref{section:2_by_2_games} and results for case (v) are presented
  in section~\ref{section:donation}.}
  \label{table:social_dilemmas}
\end{table}

% Include discussion on each game?

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{static/expected_two_by_two_games.pdf}
\end{figure}

@@

In the game stage, each individual is randomly matched with some other
individual in the population. Their interaction lasts for a number of turns
which is not fixed but depends on the continuation probability \(\delta\). At
each turn the individuals choose between cooperation (\(C\)) and defection
(\(D\)). Thus, there are four possible outcomes in each turn \(CC, CD, DC\) and
\(DD\). If both players cooperate they receive the reward payoff \(R\), whereas
if both players defect they receive the punishment payoff \(P\). If one
cooperates but the other defects, the defector receives the temptation to
defect, \(T\), whereas the cooperator receives the sucker's payoff, \(S\).
Let $\mathcal{U}=\{R,S,T,P\}$ denote the set of feasible payoffs in each round,
and let $\mathbf{u}\!=\!(R,S,T,P)$ be the corresponding payoff vector.
The values of the payoffs are not only based on the prisoner's dilemma but all
the symmetric \(2 \times 2\) games, Table~\ref{table:social_dilemmas}.

### 2021-05-05 static/last_rounds_matches.tex
writting results part two

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 5cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}
; 
\end{tikzpicture}
\end{document}

>>>>

\begin{document}
\begin{tikzpicture}[->,>=stealth',
    level/.style={sibling distance = 5cm/#1,
    level distance = 1.7cm},
    level 2/.style = {sibling distance = 2cm, level distance=2.8cm},
    every node/.style = {font=\tiny}]
\node [arn_n] {} 
    child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{SR} - S_{SM}$\\$S_{R} - S_{R}$}] {} edge from parent node[above left, rotate=30] {$\frac{1}{N - 1}$}}
    child{ node [arn_n, rotate=-30] {} 
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=39] {$\frac{(N-k-1)(N-k-2)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{M}$}] {} edge from parent node[above, yshift=-.2cm, rotate=67] {$\frac{(N-k-1)(k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{M}$\\$S_{M} - S_{R}$}] {} edge from parent node[above, yshift=-.2cm, rotate=-67] {$\frac{(k-1)(N-k-1)}{(N-2)(N-3)}$}}
            child{ node [arn_r, label={[align=center, yshift=-.8cm]$S_{R} - S_{R}$\\$S_{R} - S_{R}$}] {} edge from parent node[above, yshift=-.1cm, rotate=-41] {$\frac{(k-1)(k-2)}{(N-2)(N-3)}$}}
            edge from parent node[above left, xshift=1em, yshift=-.8em, rotate=-30] {$1 - \frac{1}{N - 1}$}
		}
; 
\end{tikzpicture}
\end{document}
